---
title: "Exploring Data Files"
author: "Jason Hunter and Ryan Greer"
date: "`r Sys.Date()`"
output: 
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This document explores the data files in the `results` and `data` folders.

## Loading Required Libraries
```{r load-libraries}
library(tidyverse)
library(readr)
```

#### Read in rlog_counts_all.rds

```{r rlog_counts_all}
rlog_counts_all <- readRDS("data/rlog_counts_all.rds")
head(rlog_counts_all)
summary(rlog_counts_all)
```

#### Read in rlog_counts_mouse_dox_long.rds
```{r rlog_counts_mouse_dox_long}
rlog_counts_mouse_dox_long <- readRDS("data/rlog_counts_mouse_dox_long.rds")
head(rlog_counts_mouse_dox_long)
summary(rlog_counts_mouse_dox_long)
```

#### Read in count_files.RData
```{r count_files}
count_files <- load("data/count_files.RData")
count_files

## this loaded in the following objects:
# counts_filtered
# counts_matrix
# g2s
```

#### Checking out the counts_filtered object
```{r counts_filtered}
head(counts_filtered)
summary(counts_filtered)
```

#### Checking out the counts_matrix object
```{r counts_matrix}
head(counts_matrix)
summary(counts_matrix)
```

#### Checking out the g2s object
```{r g2s}
head(g2s)
summary(g2s)
```

#### Reading in dds_time_point_mouse_dox_long.RData
```{r dds_time_point_mouse_dox_long}
dds_time_point_mouse_dox_long <- load("data/dds_time_point_mouse_long.RData")
dds_time_point_mouse_dox_long

## this loaded in the dds_time_point object
## let's see whats in it
head(dds_time_point)
summary(dds_time_point)
```

#### Reading in deseq_samples.RData
```{r deseq_samples}
deseq_samples <- load("data/deseq_samples.RData")
deseq_samples

head(deseq_samples)
summary(deseq_samples)
```

#### Lastly from the data folder, lets read in the time_point_res_df.RData file
```{r time_point_res_df}
time_point_res_df <- load("results/time_point_res_df.RData")
time_point_res_df

## this loaded in the res_df object
head(res_df)
summary(res_df)
```

#### There's also a results folder with some files in it.
```{r salmon.merged.gene_counts.tsv}
gene_counts <- read_tsv("results/salmon.merged.gene_counts.tsv")
head(gene_counts)
summary(gene_counts)
```

```{r salmon.merged.gene_tpm.tsv}
gene_tpm <- read_tsv("results/salmon.merged.gene_counts.tsv")
head(gene_tpm)
summary(gene_tpm)
```

```{r counts_results_DESEQ}
deseq_results <- load("results/counts_results_DESEQ/DESEQ_results.rdata")
view(deseq_results)
```

```{r TPM_results}
tpm_results <- load("results/TPM_results/TPM_results.rdata")
view(tpm_results)
```


